Apparent preferences for cognitive effort fade when multiple forms of effort

### 2020-11-23 Cost_manuscript.Rmd
minor clinical deets

``` {r BTW: 16.2.2. rmANOVA plot, echo = FALSE, fig.align = "center", fig.width = 10, fig.height = 6}
# # code to calculate the rwd/sec rate for each acceptance threshold per handling (calculate the optimal solution)
# rwd <- c(4, 8, 20)
# handling <- c(14, 10, 2) + 2 # add 2 to H and T to account for offer and reward disclosure windows
# travel <- c(2, 6, 14) + 2
# rwdRates <- sapply(3:1, function(thresh) {(sum(tail(rwd, n = thresh))) / ((handling * thresh) + (travel * 3))})
# 
# as_tibble(rwdRates) %>% 
#   mutate(Handling = handling) %>%
#   rename(Five = V1,
#          Eight = V2,
#          Twenty = V3) %>%
#   gather(Reward, Rate, -Handling) %>%
#   mutate(Reward = factor(Reward, levels = list("Five", "Eight", "Twenty")),
#          Handling = as.character(Handling)) %>%
#   group_by(Handling) %>%
#   mutate(Optimal = ifelse(Rate == max(Rate), max(Rate), -1)) %>%
#   ungroup() %>%
#   ggplot(aes(Reward, Rate, group = Handling, color = Handling)) +
#     geom_point(size = 3) +
#     geom_line(size = 1.5) +
#     geom_point(aes(Reward, Optimal), pch = 21, color = "black", fill = NA, size = 7, show.legend = F) +
#     scale_color_manual(values = c("purple", "grey50", "darkgoldenrod3")) +
#     ylim(0, 1.2) +
#     labs(y = "Expected reward per sec.", x = "Reward acceptance threshold") +
#     theme(legend.position = c(0.85, 0.2),
#           legend.key = element_blank(),
#           panel.grid.major = element_blank(), 
#           panel.grid.minor = element_blank(), 
#           panel.background = element_blank(), 
#           axis.line = element_line(colour = "black"),
#           text = element_text(size = 22))

@@

.

@@

- Clinical:  Medicated patients in remission are more sensitive to effort than controls (and are not as motivated by rewards?), and this sensitivity is predictive of relapse [@Berwian2020]. Encouraging/increasing activities has been found to be a helpful treatment for depression [@Dimidjian2006]. Since depressed patients also show insensitivity to rewards [@Huys2013], identifying what makes effort appealing in its own right can help breach treatment-resistant cases. Our work suggests that subdividing a task can promote its pursual either by taxing working memory, counting, or simply distracting. Moreover, The concavity of value means that the motivating feeling of task completion would carry more weight as pieces rather than a big net amount (thaler). This should also hold practicality for everyday scenarios, like motivating exercise, work, etc.

@@

>>>>

``` {r BTW: 16.2.2. rmANOVA plot, echo = FALSE, fig.align = "center", fig.width = 10, fig.height = 6}
# # code to calculate the rwd/sec rate for each acceptance threshold per handling (calculate the optimal solution)
# rwd <- c(4, 8, 20)
# handling <- c(14, 10, 2) + 2 # add 2 to H and T to account for offer and reward disclosure windows
# travel <- c(2, 6, 14) + 2
# rwdRates <- sapply(3:1, function(thresh) {(sum(tail(rwd, n = thresh))) / ((handling * thresh) + (travel * 3))}) 
# mean(apply(rwdRates, 1, max))
# 
# as_tibble(rwdRates) %>% 
#   mutate(Handling = handling) %>%
#   rename(Five = V1,
#          Eight = V2,
#          Twenty = V3) %>%
#   gather(Reward, Rate, -Handling) %>%
#   mutate(Reward = factor(Reward, levels = list("Five", "Eight", "Twenty")),
#          Handling = as.character(Handling)) %>%
#   group_by(Handling) %>%
#   mutate(Optimal = ifelse(Rate == max(Rate), max(Rate), -1)) %>%
#   ungroup() %>%
#   ggplot(aes(Reward, Rate, group = Handling, color = Handling)) +
#     geom_point(size = 3) +
#     geom_line(size = 1.5) +
#     geom_point(aes(Reward, Optimal), pch = 21, color = "black", fill = NA, size = 7, show.legend = F) +
#     scale_color_manual(values = c("purple", "grey50", "darkgoldenrod3")) +
#     ylim(0, 1.2) +
#     labs(y = "Expected reward per sec.", x = "Reward acceptance threshold") +
#     theme(legend.position = c(0.85, 0.2),
#           legend.key = element_blank(),
#           panel.grid.major = element_blank(), 
#           panel.grid.minor = element_blank(), 
#           panel.background = element_blank(), 
#           axis.line = element_line(colour = "black"),
#           text = element_text(size = 22))

@@

@@

- Clinical: Te motivation to exert effort or wait for delays is a distinguishing factor among mental afflictions like depression and schizophrenia [@Barch2019]. Within the former, medicated patients in remission are more sensitive to effort than controls (and are not as motivated by rewards?), and this sensitivity is predictive of relapse [@Berwian2020]. Encouraging/increasing activities has been found to be a helpful treatment for depression [@Dimidjian2006]. Since depressed patients also show insensitivity to rewards [@Huys2013], identifying what makes effort appealing in its own right can help breach treatment-resistant cases. Our work suggests that subdividing a task can promote its pursual either by taxing working memory, counting, or simply distracting. Moreover, The concavity of value means that the motivating feeling of task completion would carry more weight as pieces rather than a big net amount (thaler). This should also hold practicality for everyday scenarios, like motivating exercise, work, etc.

@@

- It's maybe relevant that waiting is goal oriented (you don't sit around for its own sake), but activities are pursued for their own appeal. *like, waiting is a goal oriented activity, but effort can be the goal itself.* in this sense it makes sense to study delays in terms of their modulation of the value of prospects, but we have unnecessarily adopted this view for ethe study of ffort, thinking of it mostly as a cost. Even if their discounting properties are similar, their resulting behavior can be contrasting (apathy vs impulsivity), and they're impacted differently by mental illness (adhd amygdala paper). Also, it's not just that we would rather to fill in empty periods of waiting, but how.
